Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-14 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Single subsection removed
Closes #74
Volunteer´s Safety
Closes #76

The web used as a resource for distributed computing has a
long history, and almost since the beginning it was used for
evolutionary computation even before JavaScript was
introduced as a browser-based scripting language in 1997. Before that
time other technologies,
 including Flash animations and VBScript, ActiveX or Java applets were
used; for instance, Java was pointed out in \cite{soares1998get} as a
``language for the
internet'', providing some advantages such as multi-architecture compatibility or
security mechanisms, and was proposed in \cite{chandy1996world} as the
basis for the creation of a world-wide peer to peer system using compiled Java
programs. The ATLAS system
\cite{Baldeschwieler:1996:TIG:504450.504482} also used Java together
with another language called Cilk; all these papers indicated that
the introduction of an architecture-independent system such as the
Java virtual machine opened the doors for ultrascale, Internet-wide,
metacomputers. This paper also establishes the desirable features of
any {\em global computing} infrastructure, that can also be applied to
distributed evolutionary computation experiments that rely on
volunteer computing: scalability, heterogeneity, fault tolerance,
adaptive parallelism, safety, anonymity, hierarchy, ease of use, and
reasonable performance. But hierarchy, this is, the capability of
preferentially using resources in the same organization, is a feature
that could be either disregarded or included within adaptivity, which
leaves us with eight desirable properties. 
% (Paloma) Re-write. For example, "But is hierarchy, this is, the
% capability of preferentially using resources in the same
% organization, the one that could be either disregarded or included
% in adaptivity, which leaves us with eight desirable properties." 
% (Paloma) And I re-wrote what I proposed yesterday.
% thanks :-) -JJ

@@

\subsection{Volunteer evolutionary computation: first experiments and results}

>>>>

The web used as a resource for distributed computing has a
long history, and almost since the beginning it was used for
evolutionary computation even before JavaScript was
introduced as a browser-based scripting language in 1997. Before that
time other technologies,
 including Flash animations and VBScript, ActiveX or Java applets were
used; for instance, Java was pointed out in \cite{soares1998get} as a
``language for the
internet'', providing some advantages such as multi-architecture compatibility or
security mechanisms, and was proposed in \cite{chandy1996world} as the
basis for the creation of a world-wide peer to peer system using compiled Java
programs. The ATLAS system
\cite{Baldeschwieler:1996:TIG:504450.504482} also used Java together
with another language called Cilk; all these papers indicated that
the introduction of an architecture-independent system such as the
Java virtual machine opened the doors for ultrascale, Internet-wide,
metacomputers. This paper also establishes the desirable features of
any {\em global computing} infrastructure, that can also be applied to
distributed evolutionary computation experiments that rely on
volunteer computing: scalability, heterogeneity, fault tolerance,
adaptive parallelism, volunteer's safety, anonymity, hierarchy, ease of use, and
reasonable performance. But hierarchy, this is, the capability of
preferentially using resources in the same organization, is a feature
that could be either disregarded or included within adaptivity, which
leaves us with eight desirable properties. 
% (Paloma) Re-write. For example, "But is hierarchy, this is, the
% capability of preferentially using resources in the same
% organization, the one that could be either disregarded or included
% in adaptivity, which leaves us with eight desirable properties." 
% (Paloma) And I re-wrote what I proposed yesterday.
% thanks :-) -JJ

@@
